\section{Abstract}
Hockey is a national sport that provides entertainment as well as exercise. Training for hockey occurs year round and contains both on ice and off ice training periods. The key objective is to observe how well off season training (i.e. rollerblading, dry-land training) mimics the movements of ice hockey skating. The goal is to generate a system that is able to record the various movements of key muscles while also monitoring the skater’s acceleration and speed and weight distribution. This document contains the progress report for the group's fourth year engineering project. Over the past few months, the group has been working on planning and implementing a system to monitor and analyze the effectiveness of movements in training for a sport versus the playing of the sport. Following the introduction (section 2), the development plans (section 3) which outlines the developed plan for the implementation of the system, and administrative plans, such as the project timeline. In the Development Activities section (section 4), you will find the progress made on the data collection and testing plan, the software system and hardware system. In this section you will also find the variation from initial plans for each respective aspect of the project. The next steps of the project to follow in the upcoming months will be outlined in the Next Steps section (section 5). The final section will include the roles of each project team member up to the point of this report (section 6), followed by the conclusion (section 7). 

\section{Introduction}
\setlength{\parindent}{5ex}
\pagenumbering{arabic}
\indent
Since the submission of the project proposal, the project team has been working hard at developing the system outlined, in order to begin data collection and analysis. For the development portion of the project, the team has been equally divided into two teams specializing on Hardware and Software, respectively. The hardware team has been developing the physical data collection prototype, while the software team has been developing the data storage, monitoring and analysis tooling. 
