\section{Objective}
\setlength{\parindent}{5ex}
\pagenumbering{arabic}
\indent
Hockey is a national sport that provides entertainment as well as exercise. Training for hockey occurs year round and contains both on ice and off ice training periods. The key objective is to observe how well off season training (i.e. rollerblading, dryland training) mimics the movements of ice hockey skating. The goal is to generate a system that is able to record the various movements of key muscles while also monitoring the skater's acceleration and speed and weight distribution.
\section{Introduction}
This document contains the project proposal for the group's fourth year engineering project. Over the next two semesters the group will work towards creating a product that can evaluate if a person off ice training is accurately depicting their on-ice work.  Following the introduction section, the proposal contains background research. This section contains some relevant information about training, electronics and muscles. The background is followed by a project description which contains what the plans for the project are. Following this section is the program relations where it will be discussed how this project relates to each person’s degree and how the team’s collective knowledge and skills will help complete the project.. Then the problem solving methods for potential issues in the project are discussed. Following this, is the group timeline that was set for the year and then the risk mitigation section will discuss potential hazards and mitigation techniques. Electronics, software and facilities required for the project will be discussed in the Electronics, software and facilities requirements section. Finally the Roles and references where the member rolls are defined and the resources accessed in the document are referenced.