\section{Next Steps}

The team will continue working on the development of the Data Collection and Monitoring Web App. The next steps for the application consist of assembling all the individual pages, and developing the functionality that will permit data to be stored on the data history page. The team will also work on formatting and connecting a database to store all historical data. Once those steps are complete, the application should be fully functional for testing and data collection. 

The next steps on the hardware side are to get all the sensors working concurrently and transmitting data to ThingSpeak. Once all sensors are working concurrently, the system will be configured for wearability for the test participants and ready for testing.   

Due to the current circumstances surrounding COVID-19 lockdowns in the region, the team has prepared a contingency plan. Since it is winter the team will shift to using outdoor public skating rinks. This will introduce challenges as the ice quality will be severely reduced on outdoor rinks, and whether conditions can be a large factor that may affect the ability to collect data and the quality of data being collected. When using the outdoor rinks there will not be previously existing markers that are on an indoor ice rink. In order to perfectly mimic these marks for the outdoor rinks, the team will be using markers and pylons in order to effectively execute the planned testing drills. For the dry-land aspect of the data gathering, the team will be attempting to utilize snow-cleared parking lots. Again, these conditions are not ideal, however due to the circumstances and budgetary constraints of the team, it is the most reasonable backup option. Of course, if the lockdown is no longer active by the time the team reaches the data gathering steps then they will continue on with their original plans and conduct the proceeding experiments inside, when possible. 
